---
title: "MT Cars"
author: "Bastiaan Quast"
date: "Thursday, July 17, 2014"
output:
  ioslides_presentation:
    transition: faster
runtime: shiny
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

```{r echo=FALSE}
library(knitr)
library(ggvis, warn.conflicts = FALSE)
library(shiny)
library(dplyr, warn.conflicts = FALSE)
```

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE, message = FALSE}
suppressWarnings(library(ggvis))
mtcars %>% ggvis(x = ~wt, y = ~mpg) %>%
  layer_points() %>%
  layer_smooths()
```

## An interactive plot:

```{r, echo = FALSE, message = FALSE, fig.width = 6, fig.height = 4}
cocaine %>%
  ggvis(x = ~potency) %>%
  layer_histograms(binwidth = input_slider(1, 20, value = 5, label = 'adjust the binwidth'))  
```


## An interactive table:

```{r, echo=FALSE, fig.width = 8, fig.height = 6}
cocaine %>%
  group_by(state) %>%
  summarise(potency = mean(potency), weight = mean(weight)) %>%
  renderDataTable()
```